---
title: "p8105_hw5_kb3066"
author: "Kaila Boyer"
date: "11/15/2021"
output: github_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(rvest)
library(httr)
library(ggpubr)

knitr::opts_chunk$set(
  fig.width = 7,
  fig.asp = .7,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis",
  scale_colour_discrete = scale_colour_viridis_d,
scale_fill_discrete = scale_fill_viridis_d
)
```

## Problem 1 

The raw data includes the column names in the first row and all entries in the lines below. Entries are separated by commas and they do not align into neat columns so it is difficult to see what each is representing. Collected data includes city, date, location coordinates, disposition, along with victim's information (name, sex, age, race)
```{r, message = F}
wash_post <- "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

post_df <- wash_post %>% url %>% read_csv()

post_df <- post_df %>% mutate(
  city_state = str_c(city, state, sep = ",")
)

post_df <- post_df %>% select(city_state, disposition) %>% 
  mutate(disp = if_else(disposition == "Open/No arrest", "unsolved", 
                if_else(disposition == "Closed without arrest", "unsolved", "solved"))) %>% 
  group_by( disp, city_state) %>% 
  count() %>% 
  pivot_wider( 
    names_from = "disp", 
    values_from = "n") %>% 
  mutate(total = sum(c_across(solved:unsolved), na.rm = T)) 
post_df %>% 
  knitr::kable(caption = "Unsolved cases by state")
```

```{r, message = F}
baltimore <- post_df %>% filter(city_state == "Baltimore,MD") 

prop.test(baltimore$unsolved, baltimore$total) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high) %>% 
  knitr::kable()
```

```{r, message = F, warning= F}
nest_post1 <- post_df %>% nest(city_state)
prop_test = function(var_numerator, var_denominator) {
  
  try(prop.test(var_numerator, var_denominator) %>% 
    broom::tidy() %>% 
    select(estimate, conf.low, conf.high), silent = TRUE)
  
} 
post2 <- nest_post1 %>% 
  mutate(cis = map2(unsolved, total, prop_test)) %>% 
  unnest()  

post2 %>% select(city_state, estimate, conf.low, conf.high) %>% knitr::kable()

post2 %>% select(city_state, estimate, conf.low, conf.high) %>%
  arrange(desc(estimate) )%>% 
  ggplot(aes(x = reorder(city_state, -estimate), y = estimate)) + 
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high))+
  coord_flip() +
  theme( plot.title = element_text(hjust = 0.5)) + 
  xlab("City") + 
  ylab("Proportion") +
  ggtitle("Proportion of Unsolved Homicides") 
```


## Problem 2 
```{r, message = F, warning = F}

exp <- tibble(filename = list.files('./data')) 
exp_paths <- exp  %>% mutate(filepath = paste0("data/", filename))


all_files <- exp_paths %>% mutate(data = map(exp_paths$filepath, read_csv)) 

all_files <- all_files %>% 
  mutate( arm = ifelse(startsWith(all_files$filename, "con"), "control", "experimental"), 
          id = str_sub(filename, start = 6L, end = -5L), 
          name = str_sub(filename, end = -5L))  



data1 <- all_files %>% 
  bind_cols(map_df(all_files$data, unlist)) %>% 
  select(-(filename:data)) %>% 
  select(id, everything())

data_long <- data1 %>% select(name, week_1:week_8, arm) %>% 
  pivot_longer(
    cols = c(week_1, week_2, week_3, week_4, week_5, week_6, week_7, week_8), 
    names_to = "week", 
    values_to = "value")
data1 %>% select(name, week_1:week_8, arm ) %>% 
  pivot_longer(
    cols = c(week_1, week_2, week_3, week_4, week_5, week_6, week_7, week_8), 
    names_to = "week", 
    values_to = "value")

by_arm <- data_long %>%  group_by(name) %>%  
  ggplot(aes( x= week, y = value, color = as.factor(name))) + 
  geom_line(aes(group= name )) + 
  scale_x_discrete( breaks = c( )) + 
  xlab("Time") + 
  ylab("Value") + 
  scale_color_viridis_d() + 
   labs(
    color = "Subjects"
  ) + 
  facet_wrap(~arm)

combined <- data_long %>%  group_by(name) %>%  
  ggplot(aes( x= week, y = value, color = as.factor(name))) + 
  geom_line(aes(group= name )) + 
  scale_x_discrete( breaks = c( )) + 
  xlab("Time") + 
  ylab("Value") + 
  scale_color_viridis_d() + 
labs(
    color = "Subjects"
  ) 

ggarrange(combined, by_arm, common.legend = TRUE, legend = "bottom")
```
The control group values are lower than the experimental values. There are fluctuations over time, but the experimental group increase while the controls stay relatively the same. 

## Problem 3 
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

fill_in = function(vector) {
  
  if(is.numeric(vector)) {
    
    vector = ifelse(is.na(vector), mean(vector, na.rm = TRUE), vector)
    
    }
  
  if(is.character(vector)) {
    
    vector = ifelse(is.na(vector), "virginica", vector)
    
  }
  
  return(vector)
  
}

iris_df<- map_df(iris_with_missing, fill_in) 

glimpse(iris_df)
map(iris_df, Hmisc::describe)
```


